---
title: "Buenos Aires Real Estate Map"
author: "Edwin R. Mutandi"
date: "2026-04-22"
output: html_document
---

## Overview

This webpage presents an interactive map of real estate listings in Buenos Aires using the Leaflet library in R.

**Dataset source:** Kaggle Buenos Aires Real Estate dataset.

**Created on:** `r Sys.Date()`

---

## Load Required Libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(leaflet)
library(dplyr)
library(readr)
```

---

## Load Dataset

> Ensure the CSV file is in the same folder as this R Markdown file.

```{r}
data <- read_csv("buenos-aires-real-estate.csv")
```

---

## Data Cleaning

> Dataset already uses `lat` and `lon`, so no renaming is required.

```{r}
data_clean <- data %>%
  filter(!is.na(lat), !is.na(lon))
```

---

## Interactive Leaflet Map

```{r}
leaflet(data_clean) %>%
  addProviderTiles(providers$OpenStreetMap) %>%
  setView(
    lng = mean(data_clean$lon, na.rm = TRUE),
    lat = mean(data_clean$lat, na.rm = TRUE),
    zoom = 10
  ) %>%
  addCircleMarkers(
    lng = ~lon,
    lat = ~lat,
    radius = 5,
    stroke = FALSE,
    fillOpacity = 0.7,
    popup = ~paste0(
      "<b>Price:</b> ", 
      if ("price" %in% names(data_clean)) {
        ifelse(is.na(price), "N/A", price)
      } else {
        "N/A"
      },
      "<br>",
      "<b>Property Type:</b> ", 
      if ("property_type" %in% names(data_clean)) {
        ifelse(is.na(property_type), "N/A", property_type)
      } else {
        "N/A"
      }
    )
  )
```

---

## Notes

- Each marker represents a property listing
- Click markers to view property details
- The map supports zooming and panning (interactive Leaflet features)

---

## Reproducibility

To reproduce this project:

1. Install required packages:

```r
install.packages(c("rmarkdown", "leaflet", "dplyr", "readr"))
```

2. Download dataset from Kaggle:  
https://www.kaggle.com/datasets/dataenthusiast947/buenos-aires-real-estate

3. Place the CSV file in your working directory

4. Knit this document to HTML


